---
output: github_document
editor_options: 
  chunk_output_type: inline
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)

library(emo)
```

# dmc

<!-- badges: start -->
[![Travis build status](https://travis-ci.org/sharlagelfand/dmc.svg?branch=master)](https://travis-ci.org/sharlagelfand/dmc)
[![Codecov test coverage](https://codecov.io/gh/sharlagelfand/dmc/branch/master/graph/badge.svg)](https://codecov.io/gh/sharlagelfand/dmc?branch=master)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->

The goal of dmc is to allow you to find the closest DMC embroidery floss colour(s) for a given colour, as well as access colour (hex, RGB) information about DMC colours.

If you'd like to use dmc without having to install the package (or R!), there is a [Shiny app](https://sharlagelfand.shinyapps.io/dmcapp/) as well (in its own package, [dmcapp](https://github.com/sharlagelfand/dmcapp)).

## Installation

You can install the development version of dmc from github with:

``` r
# install.packages(devtools)
devtools::install_github("sharlagelfand/dmc")
```

## Example

Say I'm interested in finding the closest DMC floss colour for the background colour of the [`dplyr` package's hex logo](https://github.com/tidyverse/dplyr/blob/master/man/figures/logo.png) `r emo::ji("smiling_imp")`.

I can look up the hex code for this colour via a site like [HTML Color Codes](https://html-colour-codes.info/colours-from-image/). The hex code is "#EE8726".

Then, I can use `dmc()` to find the closest DMC floss for this colour:

```{r dmc-dplyr}
library(dmc)

dplyr_background <- "#EE8726"

dmc(dplyr_background)
```

I can choose to show more than one matching colour:

```{r dmc-dplyr-3}
dmc(dplyr_background, n = 3)
```

And to turn off the visualization of the colours:

```{r dmc-dplyr-no-vis}
dmc(dplyr_background, visualize = FALSE)
```

By default, `dmc()` uses Euclidean distance to find the closest floss colour. The method can be changed to be one of "euclidean", "cie1976", "cie94", "cie2000", or "cmc". For example:

```{r dmc-dplyr-cie94}
dmc(dplyr_background, n = 3, method = "cie94")
```

If I want to go the *other* way and just find the hex/RGB information for a given DMC floss, I can use `undmc()`. By default, this visualizes the DMC floss:

```{r undmc}
undmc(c("Ecru", "B5200"))
```

Again, the visualization can be turned off:

```{r undmc-no-viz}
undmc(310, visualize = FALSE)
```

`undmc()` mostly just takes the DMC floss number, except in cases where there isn't one (e.g., Ecru).

A full list of floss colours in the package is available via `floss`:

```{r floss}
floss
```

where the values in `floss[["dmc"]]` are all that can be passed to `undmc()`.
